### 2022-01-19 response2/response2.tex
Corrections

The accessibility of coherent driving fields such as laser opens many interesting capabilities for manipulating quantum systems. This leads to the Floquet engineering of solid-state, atomic, and photonic systems with the basics of Floquet states. In general, the powerful thermodynamic rules related to the static systems in thermal equilibrium, cannot be applied to the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}. Therefore, to achieve the viability of Floquet engineering in fermion systems, it is crucial to understand the conditions for a steady-state particle distribution and it is one of the main challenges in the field. Among previous studies on this topic, a major point of investigation is time scales. As an example, if the switch-on of the driving field is not far from the past, the distribution function of a quantum system will highly depend on the switching-on protocol of the periodic driving \cite{dehghani2014}. Although we can consider the intermediate timescales, there would be many physical processes causing the heating of the quantum system. A variety of approaches for stabilizing the quantum system under this condition have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}. When the applied driving field gets more powerful the heating caused by the field gets increases. Thus, the cooling system needs to be much stronger and this leads to a non-perturbative inclusion of the bath in the system. In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasiparticles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
However, a fully microscopic description of the heating of a driven system is a rather challenging task due to the multiple processes that need to be investigated.
It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging. In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy densty \cite{rudner2020}. This leads towards a featureless state at long times. All these conclude that understanding heating processes in any timescale and addressing them to describe a realistic driven system needs the treatment of very rich physics. However, under proper parameter regimes to be discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.

@@

\begin{itemize}
  \item Section V - second paragraph (page 7):\\
  {\color{Red}
  To further evaluate the conductivity expression, we must specify the distribution function. Generic interacting Floquet systems absorb photons from the radiation and tend to heat up \cite{seetharam2019,rudner2020}.
  However, a full description of a common dressed system requires a proper treatment of photon interactions. The complexity attached to these interactions is very high. There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving nonequilibrium steady-state distribution. Working in regimes where heating rates are strongly suppressed enables steady particle distribution function in driven isolated quantum systems. However, a full description of a common dressed system requires a proper treatment of photon interactions. The complexity attached to these interactions is very high.
  As mentioned in Rudner \textit{et al.} \cite{rudner2020}, placing proper conditions on energy and time scales, the distribution function of a Floquet system can be assumed to be steady. By properly selecting the frequency of the radiation, we can ensure that the interband electron transitions are controlled. This leads to significantly suppressed heating rates.
  Let's consider our dressed quantum Hall system under off-resonant conditions \cite{rudner2020,wackerlthesis20}, where photon absorption does not happen. Thus, we can assume that the driving field only renormalizes the system's parameters rather than changing the particle distribution function.
  Additionally, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our Floquet system
  \begin{equation} \tag{33}
    f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
  \end{equation}
  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system. To compare our results with the outcomes already known in the literature \cite{dini16,endo09}, we enforce the low-temperature conditions to the Fermi-Dirac distribution.
  At low-temperatures conditions, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
  \begin{equation} \tag{34}
    - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
  \end{equation}
  }
\end{itemize}

\subsubsection*{Comment 2 -
\color{RoyalBlue} Moreover, the authors are misinterpreting the results of earlier theoretical works. In particular, Ref. [31] demonstrates both the effect of photo excitations of electrons and the dressing of electronic states.}

@@

{\color{CadetBlue} “This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs [54-57]. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
The influence induced by a pure dressing field on
magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.”}

@@

What we meant to say here is that work presented in Dmitriev \textit{et al.} \cite{dmitriev09} related to the microwave-induced resistance oscillations (MIROs) that can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation. As mentioned by the reviewer, Ref. \cite{dmitriev09} have appropriately described the magneto-transport properties using the dressed states of electrons as well as the photon interactions. On the other hand, if the driving field is in a high-frequency regime, we can neglect the photon interactions as mentioned in the response to the first comment. In addition, we can identify that the high-frequency and low-frequency radiation lead to two different behaviors of the magneto-transport characteristics of dressed quantum Hall systems \cite{dini16}. With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can observe increased longitudinal conductivity. However, we can predict a depletion of both the broadening of Landau levels and the longitudinal conductivity under high-frequency radiation.
Our analysis is focused on a high-frequency regime where we can significantly suppress the photon interactions in the Floquet system. Therefore, we meant to mention this difference between our study and the Ref. \cite{dmitriev09}. We never meant to say that Dmitriev \textit{et al.} \cite{dmitriev09} only consider the effects of photon excitations.

@@

\begin{itemize}
  \item Section I - second paragraph (page 5):\\
  {\color{Red}
  This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to the effects of low-frequency (microwave) electromagnetic fields that increase the longitudinal conductivity.
  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduces the longitudinal conductivity \cite{dini16}.
  Since high-frequency radiation only contributes to the suppression of electron scattering, the driving field can be treated as a pure dressing (nonabsorbable) field \cite{dini16}.
  Thus, the influence induced by a high-frequency pure dressing field on
  magneto-transport properties of 2DEG quantum Hall system need to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
  }
\end{itemize}

>>>>

The accessibility of coherent driving fields such as laser opens many interesting capabilities for manipulating quantum systems. This leads to the Floquet engineering of solid-state, atomic, and photonic systems with the basics of Floquet states. In general, the powerful thermodynamic rules related to the static systems in thermal equilibrium, cannot be applied to the non-equilibrium regime where Floquet states are defined \cite{seetharam2015}. Therefore, to achieve the viability of Floquet engineering in fermion systems, it is crucial to understand the conditions for a steady-state particle distribution and it is one of the main challenges in the field. Among previous studies on this topic, a major point of investigation is time scales. As an example, if the switch-on of the driving field is not far from the past, the distribution function of a quantum system will highly depend on the switching-on protocol of the periodic driving \cite{dehghani2014}. Although we can consider the intermediate timescales, there would be many physical processes causing the heating of the quantum system. A variety of approaches for stabilizing the quantum system under this condition have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}. When the applied driving field gets more powerful the heating caused by the field gets increases. Thus, the cooling system needs to be much stronger and this leads to a non-perturbative inclusion of the bath in the system. In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasi-particles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
However, a fully microscopic description of the heating of a driven system is a rather challenging task due to the multiple processes that need to be investigated.
It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging. In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}. This leads towards a featureless state at long times. All these conclude that understanding heating processes in any timescale and addressing them to describe a realistic driven system needs the treatment of very rich physics. However, under proper parameter regimes to be discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.

@@

\begin{itemize}
  \item Section V - second paragraph (page 7):\\
  {\color{Red}
  To further evaluate the conductivity expression, we must specify the distribution function. Generic interacting Floquet systems absorb photons from the radiation and tend to heat up \cite{seetharam2019,rudner2020}.
  However, a full description of a common dressed system requires a proper treatment of photon interactions. The complexity attached to these interactions is very high. There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving non-equilibrium steady-state distribution. Working in regimes where heating rates are strongly suppressed enables steady particle distribution function in driven isolated quantum systems. However, a full description of a common dressed system requires a proper treatment of photon interactions. The complexity attached to these interactions is very high.
  As mentioned in Rudner \textit{et al.} \cite{rudner2020}, placing proper conditions on energy and time scales, the distribution function of a Floquet system can be assumed to be steady. By properly selecting the frequency of the radiation, we can ensure that the inter-band electron transitions are controlled. This leads to significantly suppressed heating rates.
  Let's consider our dressed quantum Hall system under off-resonant conditions \cite{rudner2020,wackerlthesis20}, where photon absorption does not happen. Thus, we can assume that the driving field only renormalizes the system's parameters rather than changing the particle distribution function.
  Additionally, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our Floquet system
  \begin{equation} \tag{33}
    f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
  \end{equation}
  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system. To compare our results with the outcomes already known in the literature \cite{dini16,endo09}, we enforce the low-temperature conditions to the Fermi-Dirac distribution.
  At low-temperatures conditions, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
  \begin{equation} \tag{34}
    - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
  \end{equation}
  }
\end{itemize}

\subsubsection*{Comment 2 -
\color{RoyalBlue} Moreover, the authors are misinterpreting the results of earlier theoretical works. In particular, Ref. [31] demonstrates both the effect of photo excitation of electrons and the dressing of electronic states.}

@@

{\color{CadetBlue} “This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs [54-57]. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (non-absorbable) field.
The influence induced by a pure dressing field on
magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.”}

@@

What we meant to say here is that work presented in Dmitriev \textit{et al.} \cite{dmitriev09} related to the microwave-induced resistance oscillations (MIROs) that can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation. As mentioned by the reviewer, Ref. \cite{dmitriev09} have appropriately described the magneto-transport properties using the dressed states of electrons as well as the photon interactions. On the other hand, if the driving field is in a high-frequency regime, we can neglect the photon interactions as mentioned in the response to the first comment. In addition, we can identify that the high-frequency and low-frequency radiation lead to two different behaviors of the magneto-transport characteristics of dressed quantum Hall systems \cite{dini16}. With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can observe increased longitudinal conductivity. However, we can predict a depletion of both the broadening of Landau levels and the longitudinal conductivity under high-frequency radiation.
Our analysis is focused on a high-frequency regime where we can significantly suppress the photon interactions in the Floquet system. Therefore, we meant to mention this difference between our study and the Ref. \cite{dmitriev09}. We never meant to say that Dmitriev \textit{et al.} \cite{dmitriev09} only consider the effects of photon excitation.

@@

\begin{itemize}
  \item Section I - second paragraph (page 5):\\
  {\color{Red}
  This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to the effects of low-frequency (microwave) electromagnetic fields that increase the longitudinal conductivity.
  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduces the longitudinal conductivity \cite{dini16}.
  Since high-frequency radiation only contributes to the suppression of electron scattering, the driving field can be treated as a pure dressing (non-absorbable) field \cite{dini16}.
  Thus, the influence induced by a high-frequency pure dressing field on
  magneto-transport properties of 2DEG quantum Hall system need to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
  }
\end{itemize}
